\projectname: A systematic search for transits in \KT\ data

### 2015-01-27 ms.tex
nothing

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To exploit this fact, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{map-pdc1, map-pdc2}.
Similarly, we ran PCA (as implemented by the \project{scikit-learn} project
\citealt{sklearn}) on the full set of Campaign 1 light curves to determine a
basis of representative ELCs.
We chose to keep the top 200 components---many more than are normally
used---for our model described in the following section.
\dfmtodo{do we want to plot some of these light curves here?}

@@

Physically, the motivation for our model---and the PDC model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{vanderberg-a, crossfield} but out more
flexible model should capture the systematic effects more robustly but there
is a risk of over-fitting.

To avoid over-fitting in our pipeline, we simultaneously fit for the transit
signal and the trends using a rigid model for the signal and a relatively
flexible model for the noise.
Specifically, we model the light curve as being generated by linear
combination of the 200 basis light curves and a ``box'' transit model at a
given period and phase.

Then points in this space with likelihoods greater than some minimum value
could then be accepted as candidates for vetting.
This is similar (\dfmtodo{what is the exact comparison?}) to the standard
procedure of accepting candidates above some signal-to-noise threshold.
We find, however, that the procedure described in the following section is
much less sensitive to false alarms.

@@

\paragraph{Initial ``one-dimensional'' search}

\paragraph{Period \& phase search}

@@

% \begin{figure}[p]
% \begin{center}
% \includegraphics[width=\textwidth]{path/to/figure.pdf}
% \end{center}
% \caption{%
% A CAPTION.
% \figlabel{the-figure-label}}
% \end{figure}

>>>>

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To exploit this fact, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{map-pdc1, map-pdc2}.
Similarly, we ran PCA (as implemented by the \project{scikit-learn} project
\citealt{sklearn}) on the full set of Campaign 1 light curves to determine a
basis of representative ELCs.
We chose to use the top 150 components---many more than are normally
used---for our model described in the following section.
\Fig{pca} shows the top few ELCs.

@@

Physically, the motivation for our model---and the PDC model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{vanderberg-a, crossfield} but out more
flexible model should capture the systematic effects more robustly but there
is a risk of over-fitting.
\Fig{corr} shows the application of this model to a light curve with no known
transit signals.

To avoid over-fitting in our pipeline, we simultaneously fit for the transit
signal and the trends using a rigid model for the signal and a relatively
flexible model for the noise.
Specifically, we model the light curve as being generated by linear
combination of the 150 basis light curves and a ``box'' transit model at a
given period and phase.

@@

In theory, search could proceed by evaluating the model described above on a
fine grid three-dimensional grid in period, phase, and duration.
In practice, this is computationally intractable for any grids of the
required size.
Instead, we can compute the values on this grid approximately, but at very
high precision, using a two-step procedure that is much more computationally
efficient.
The first step, called the {\bf linear search}, involves hypothesizing a
single transit on a two-dimensional grid in duration and transit time.
The second step, the {\bf periodic search} uses a lookup table built on the
results of the linear search to compute the likelihood for the periodic model.
Finally, the peaks in the likelihood space are passed along for machine and
hand vetting.

\paragraph{Linear search}

The linear search involves hypothesizing a transit signal on a
two-dimensional grid in transit time and duration.
For each point in the grid, we use the model described in the previous
section to evaluate \emph{the likelihood function} of the transit depth.
Because the model is linear, the likelihood function for the depth
(marginalized over the model of the systematics) is a Gaussian:
\begin{eqnarray}
\ln \mathcal{L} (d) &\propto& \mathcal{N} ()
\end{eqnarray}

\paragraph{Periodic search}

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/pca.pdf}
\end{center}
\caption{%
A CAPTION.
\figlabel{pca}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/corr.pdf}
\end{center}
\caption{%
A CAPTION.
\figlabel{corr}}
\end{figure}
